Sparse Function-space Representation of Neural Networks

### 2023-08-30 workshops/icml-duality/main.tex
update regression fig
increase font size
placed arrow better

\begin{figure}[t!]
  \centering\scriptsize
  % Figure options
  \pgfplotsset{axis on top,scale only axis,width=\figurewidth,height=\figureheight, ylabel near ticks,ylabel style={yshift=-2pt},y tick label style={rotate=90},legend style={nodes={scale=1., transform shape}},tick label style={font=\tiny,scale=1}}
  \pgfplotsset{xlabel={Input, $x$},axis line style={rounded corners=2pt}}
  % Set figure
  \setlength{\figurewidth}{.4\textwidth}
  \setlength{\figureheight}{\figurewidth}
  %
  \def\inducing{\large Sparse inducing points}
  %
  \begin{subfigure}[c]{.52\columnwidth}
    \raggedleft
    \pgfplotsset{ylabel={Output, $y$}}
    \input{./fig/regression-nn.tex}%
  \end{subfigure}
  \hfill
  \begin{subfigure}[c]{.02\columnwidth}
    \centering
    \tikz[overlay,remember picture]\node(p0){};
  \end{subfigure}
  \hfill
  \begin{subfigure}[c]{.4\columnwidth}
    \raggedleft
    \pgfplotsset{yticklabels={,,},ytick={\empty}}
    \input{./fig/regression-nn2svgp.tex}%
  \end{subfigure}
%  \hfill
%  \begin{subfigure}[c]{.01\textwidth}
%    \centering
%    \tikz[overlay,remember picture]\node(p1){};
%  \end{subfigure}
%  \hfill
%  \begin{subfigure}[c]{.28\textwidth}
%    \raggedleft
%    \pgfplotsset{yticklabels={,,},ytick={\empty}}
%    \input{./fig/regression-update.tex}%
%  \end{subfigure}
  \vspace*{-1em}
  \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network. Right:~Our approach summarizes all the training data with the help of a set of inducing points.} %The model captures the predictive mean and uncertainty, and (right) makes it possible to incorporate new data without retraining the model.}
  \label{fig:teaser}
  %
  \begin{tikzpicture}[remember picture,overlay]
    % Arrow style
    \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=14mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
    % Arrows
    \node[myarrow] (p0-arr) at ($(p0) + (1em,1.5em)$) {};
    %\node[myarrow] (p1-arr) at ($(p1) + (1em,1.5em)$) {};
    % Arrow labels
    \node[font=\scriptsize\sc,color=white] at (p0-arr) {\our};
    %\node[font=\scriptsize\sc,color=white] at (p1-arr) {new data};
  \end{tikzpicture}
  \vspace*{-1em}
\end{figure}

>>>>

\begin{figure}[t!]
  % \centering\scriptsize
  \centering\Large
  % Figure options
  \pgfplotsset{axis on top,scale only axis,width=\figurewidth,height=\figureheight, ylabel near ticks,ylabel style={yshift=-2pt},y tick label style={rotate=90},legend style={nodes={scale=1., transform shape}},tick label style={font=\Large,scale=1}}
  \pgfplotsset{xlabel={Input, $x$},axis line style={rounded corners=2pt}}
  % Set figure
  \setlength{\figurewidth}{.4\textwidth}
  \setlength{\figureheight}{\figurewidth}
  %
  \def\inducing{\Huge Sparse inducing points}
  %
  \begin{subfigure}[c]{.52\columnwidth}
    \raggedleft
    \pgfplotsset{ylabel={Output, $y$}}
    \input{./fig/regression-nn.tex}%
  \end{subfigure}
  \hfill
  \begin{subfigure}[c]{.02\columnwidth}
    \centering
    \tikz[overlay,remember picture]\node(p0){};
  \end{subfigure}
  \hfill
  \begin{subfigure}[c]{.4\columnwidth}
    \raggedleft
    \pgfplotsset{yticklabels={,,},ytick={\empty}}
    \input{./fig/regression-nn2svgp.tex}%
  \end{subfigure}
%  \hfill
%  \begin{subfigure}[c]{.01\textwidth}
%    \centering
%    \tikz[overlay,remember picture]\node(p1){};
%  \end{subfigure}
%  \hfill
%  \begin{subfigure}[c]{.28\textwidth}
%    \raggedleft
%    \pgfplotsset{yticklabels={,,},ytick={\empty}}
%    \input{./fig/regression-update.tex}%
%  \end{subfigure}
  % \vspace*{-1em}
  \caption{\textbf{Regression example on an MLP with two hidden layers.} Left:~Predictions from the trained neural network. Right:~Our approach summarizes all the training data with the help of a set of inducing points.} %The model captures the predictive mean and uncertainty, and (right) makes it possible to incorporate new data without retraining the model.}
  \label{fig:teaser}
  %
  \begin{tikzpicture}[remember picture,overlay]
    % Arrow style
    \tikzstyle{myarrow} = [draw=black!80, single arrow, minimum height=14mm, minimum width=2pt, single arrow head extend=4pt, fill=black!80, anchor=center, rotate=0, inner sep=5pt, rounded corners=1pt]
    % Arrows
    \node[myarrow] (p0-arr) at ($(p0) + (0.2em,1.2em)$) {};
    % \node[myarrow] (p0-arr) at ($(p0) + (1em,1.5em)$) {};
    %\node[myarrow] (p1-arr) at ($(p1) + (1em,1.5em)$) {};
    % Arrow labels
    \node[font=\scriptsize\sc,color=white] at (p0-arr) {\our};
    %\node[font=\scriptsize\sc,color=white] at (p1-arr) {new data};
  \end{tikzpicture}
  \vspace*{-1em}
\end{figure}
